---
title: "Sample Code in dxpr paper"
author: Yi-Ju Tseng, Hsiang-Ju Chiu, Chun-Ju Chen
output: github_document
---
dxpr: An R package for generating analysis-ready data from electronic health records—diagnoses and procedures

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Preparation for analysis

```{r install, eval=F}
devtools::install_github("DHLab-TSENG/dxpr")
```
```{r lib}
library(dxpr)
```

# Data integration
## Code format transformation


```{r code}
ICD_Decimal <- icdDxShortToDecimal(dxDataFile = sampleDxFile,
                                   icdColName = ICD,
                                   dateColName = Date, 
                                   icd10usingDate = "2015/10/01")
sampleDxFile$Decimal <- ICD_Decimal$ICD
head(sampleDxFile)
tail(ICD_Decimal$Error)
```

## Code grouping

```{r group}
CCS_description <- icdDxToCCS(dxDataFile = sampleDxFile,
                              idColName = ID,
                              icdColName = ICD,
                              dateColName = Date, 
                              icd10usingDate = "2015-10-01", 
                              isDescription = TRUE)
CCS_description$groupedDT[CCS_description$groupedDT$ID=="A0",]

```

# Data wrangling
## Case selection
```{r case}
Case <- selectCases(dxDataFile = sampleDxFile,
                    idColName = ID,
                    icdColName = ICD, 
                    dateColName = Date, 
                    icd10usingDate = "2015/10/01",
                    groupDataType = ccslvl2,
                    caseCondition = "Diseases of the urinary system",
                    isDescription = TRUE,
                    caseCount = 1,
                    periodRange = c(30, 365)) 
head(Case)
tail(Case)
```

## Eligible period identification
```{r Eligible}
admissionDate <- getEligiblePeriod(dxDataFile = sampleDxFile,
                                   idColName = ID,
                                   dateColName = Date)
head(admissionDate) 
```

## Data splitting based on index date and moving window
```{r split}
indexDateTable <- data.frame (ID = c("A0","B0","C0","D0"),
                              indexDate = c("2023-08-12", "2015-12-26",
                                            "2015-12-05", "2017-01-29"))
Data <- splitDataByDate(dxDataFile = sampleDxFile[grepl("A0|B0|C0|D0",ID),],
                        idColName = ID,
                        icdColName = ICD,
                        dateColName = Date,
                        indexDateFile = indexDateTable,
                        gap = 30)
Data[6:11,]
```


## Condition era generation
```{r era}
Era <- getConditionEra(dxDataFile = sampleDxFile,
                       idColName = ID,
                       icdColName = ICD,
                       dateColName = Date,
                       icd10usingDate = "2015/10/01",
                       groupDataType = CCS,
                       isDescription = FALSE,
                       gapDate = 360)
head(Era)

```


## Analysis-ready data generation
```{r ARD}
CHARLSON <- icdDxToComorbid(dxDataFile = sampleDxFile,
                            idColName = ID,
                            icdColName = ICD,
                            dateColName = Date,
                            icd10usingDate = "2015-10-01",
                            comorbidMethod = CHARLSON)
groupedData_Wide <- groupedDataLongToWide(dxDataFile  = CHARLSON$groupedDT,
                                          idColName = ID,
                                          categoryColName = Comorbidity,
                                          dateColName = Date,
                                          reDup = TRUE,
                                          numericOrBinary = B,
                                          count = 2)
head(groupedData_Wide, 5)
```

# Visualization
## Pareto chart of error ICD
```{r Pareto}
error <- icdDxDecimalToShort(dxDataFile = sampleDxFile,
                             icdColName = ICD,
                             dateColName = Date,
                             icd10usingDate = "2015/10/01")
plot1 <- plotICDError(errorFile = error$Error,
                      icdVersion = all,
                      wrongICDType = all,
                      groupICD = FALSE,
                      others = TRUE, 
                      topN = 10)
plot1$graph
plot1$ICD
```


## Bar chart of diagnostic categories
```{r Bar}
ELIX <- icdDxToComorbid(dxDataFile  = sampleDxFile,
                        idColName = ID,
                        icdColName = ICD,
                        dateColName = Date,
                        icd10usingDate = "2015-10-01",
                        comorbidMethod = ELIX)
groupedDataWide <- groupedDataLongToWide(dxDataFile  = ELIX$groupedDT,
                                         idColName = ID,
                                         categoryColName = Comorbidity,
                                         dateColName = Date,
                                         reDup = TRUE,
                                         numericOrBinary = B)
plot2 <- plotDiagCat(groupedDataWide = groupedDataWide,
                     idColName = ID,
                     topN = 10,
                     limitFreq = 0.01)
plot2$graph
plot2$sigCate
```


